---
title: "Data from D.A.T.A"
author: "UniLee"
date: "2/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(foreign)
library(tidyverse)
```

Consider the dataset from Boston University's D.A.T.A on Chinese Global Investment in Energy Sector. (Source: http://www.bu.edu/gdp/research/databases/)

```{r}
a<- read.csv("BU-PITCH-EN-2020.csv", stringsAsFactors=FALSE)
```

Clean the dataset and select BRI projects only.

```{r}
a <- a %>% rename(Amount=Amount...m.)
b <- a %>% select(Country, Region, EnergySource, EnergySubSector, Lender, Amount, Description, BRI.Membership)
# ab <- b[which(a$BRI.Membership==1),]
# ab$BRI.Membership <- NULL
```

Total Amount of global BRI investment in energy sector is $183,421,000,000. 
NOTE: The number provided by the Global China Investment Tracker is $109,700,000,000. The discrepancy comes from the fact that the Global China Investment Tracker excludes "troubled transactions" and "contracts". Compare the datasets here. https://www.aei.org/china-global-investment-tracker/

```{r}
sum(b$Amount)
```

Regional breakdown of BRI  projects

```{r}
Region_percent <- b %>% group_by(Region) %>% 
  summarise(subtotal_region = sum(Amount)) %>% 
  mutate(regional_share = subtotal_region/sum(subtotal_region)*100) %>% 
  arrange(desc(regional_share))
Region_percent
```

Breakdown of BRI projects by Technology

```{r}
Tech_percent <- b %>% group_by(EnergySource) %>% 
  summarise(subtotal_tech = sum(Amount)) %>% 
  mutate(tech_share = subtotal_tech/sum(subtotal_tech)*100) %>% 
  arrange(desc(tech_share))

Tech_percent

Tech_pie <- b %>% group_by(EnergySource) %>% 
  summarise(subtotal_tech = sum(Amount))
techpiechart <- ggplot(Tech_pie,aes(x="", y=subtotal_tech, fill=EnergySource)) + 
  geom_bar(width=1, stat="identity") + coord_polar("y") +
  geom_text(aes(label = paste0(round(subtotal_tech/sum(subtotal_tech)*100), "%")), position = position_stack(vjust = 0.5)) + 
  scale_fill_hue() + 
  labs(x = NULL, y = NULL, fill = NULL, title = "Investment by Energy Source") + 
  theme_classic() + theme(axis.line = element_blank(),
                                    axis.text = element_blank(),
                                    axis.ticks = element_blank(),
                                    plot.title = element_text(hjust = 0.5, color = "#666666"))

techpiechart
```

What kind of projects are there? 

```{r}
sector <- b %>% group_by(EnergySubSector) %>% 
  summarise(subtotal_sector=sum(Amount)) %>% 
  mutate(sector_share=subtotal_sector/sum(subtotal_sector)*100) %>% 
  arrange(desc(sector_share))

sector
```
```{r}
sectorpie <- b %>% group_by(EnergySubSector) %>% 
  summarise(subtotal_sector=sum(Amount))

sectorpiechart <- ggplot(sectorpie,aes(x="", y=subtotal_sector, fill=EnergySubSector)) + 
  geom_bar(width=1, stat="identity") + coord_polar("y") +
  geom_text(aes(label = paste0(round(subtotal_sector/sum(subtotal_sector)*100), "%")), position = position_stack(vjust = 0.5)) + 
  scale_fill_brewer() + 
  labs(x = NULL, y = NULL, fill = NULL, title = "Investment by Energy Subsector") + 
  theme_classic() + theme(axis.line = element_blank(),
                                    axis.text = element_blank(),
                                    axis.ticks = element_blank(),
                                    plot.title = element_text(hjust = 0.5, color = "#666666"))
sectorpiechart
```



The biggest BRI investment is made in Russia, in an exploration and extraction for oil.

```{r}
ab[which.max(ab$Amount),]
```
There is only one project in East Asia: grid project in Monolia. 
```{r}
ab %>% filter(Region=="East Asia")

```
The list of BRI solar and wind projects are as follows, in descending order. 

```{r}
ab %>% filter(EnergySource=="Solar" | EnergySource=="Wind") %>% arrange(desc(Amount))
```
China has 3 nuclear projects in Pakistan. 

```{r}
ab %>% filter(EnergySource=="Nuclear") %>% arrange(desc(Amount))
```

```{r}
c <- a %>% select(Date, Amount) %>% 
  group_by(Date) %>% summarise(annual_investment = sum(Amount)) 
ggplot(c, aes(x=Date, y=annual_investment)) + geom_col() + xlab("Annual Investment") + ylab("Year")
```

Solar and Wind for all investments

```{r}
e<- read.csv("BU-PITCH-EN-2020.csv", stringsAsFactors=FALSE)
e <- a %>% rename(Amount=Amount...m.)
e <- a %>% select(Country, Region, EnergySource, EnergySubSector, Lender, Amount, Description, BRI.Membership)
names(e)
solarwind <- e %>% filter(EnergySource=="Solar" | EnergySource=="Wind") %>% arrange(desc(Amount))
solarwind

```



