---
title: "CHIT"
author: "UniLee"
date: "2/21/2020"
output: html_document
---
rm(list = ls())
library(dplyr)
library(stringr)
library(foreign)
a<-read.csv("chitfull.csv", skip=5, stringsAsFactors=F)

a$Quantity.in.Millions <- str_replace_all(a$Quantity.in.Millions, ",", "")
a$Quantity.in.Millions <- as.numeric(str_replace_all(a$Quantity.in.Millions, "\\$", ""))
# a$Energy <- ifelse(a$Sector=="Energy", a$Quantity.in.Millions, NA)
TotalInvestment <- sum(a$Quantity.in.Millions)

BRI <- a %>% filter(BRI==1)
TotalBRI <- sum(BRI$Quantity.in.Millions)

```{r}
TotalInvestment
```
```{r}
TotalBRI
```
```{r}
TotalBRI/TotalInvestment*100
```
Energy <- a %>% filter(Sector=="Energy")
AllEnergy <- sum(Energy$Quantity.in.Millions)

```{r}
AllEnergy
```
```{r}
AllEnergy/TotalInvestment*100
```

In which region are they investing in? 

```{r}
all_by_region <- a %>% group_by(Region) %>% 
  summarise(region_subtotal=sum(Quantity.in.Millions),
          energy_by_region=sum(Quantity.in.Millions[Sector=="Energy"])) %>% 
  mutate(regionshare=region_subtotal/sum(region_subtotal)*100,
         region_e_share=energy_by_region/sum(energy_by_region)*100) %>% 
  arrange(desc(regionshare)) 

all_by_region
```

In which sector are they investing in? 

```{r}
all_by_sector <- a %>% group_by(Sector) %>% 
  summarise(sector_subtotal=sum(Quantity.in.Millions)) %>% 
  mutate(sector_share=sector_subtotal/sum(sector_subtotal)*100) %>% 
  arrange(desc(sector_share))
all_by_sector
```


